---
title: "Untitled"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{css echo=FALSE}
ins, del{
  text-decoration: none;
  display: inline-block;
  padding: 0 .3em;
}
ins {
  background: #83d5a8;
  height: auto;
  border-radius: .3em;
  display: inline; 
  -webkit-box-decoration-break: clone;
  -o-box-decoration-break: clone;
  box-decoration-break: clone;
  margin-left: .07em;
  margin-right: .07em;
}
del {
  background: rgba(231, 76, 60,.5);
  cursor: no-drop;
  position: relative;
  top: .2em;
  height: 1.31em;
  width: .4em;
  line-height: 1.35;
  overflow: hidden;
  color: transparent;
  margin: -.4em .07em -.05em .07em;
  padding: 0 0 .1em 0;
  -webkit-box-decoration-break: clone;
  -o-box-decoration-break: clone;
  box-decoration-break: clone;
  border-radius: .3em;
  transition: padding-left ease .3s, padding-right ease .3s, color ease .15s;
}
del:hover {
  width: auto;
  color: #962e22;
  display: inline;
  padding: 0 .35em 0em 0.35em;
  line-height: unset;
  position: unset;
  top: unset;
  height: unset;
  transition: padding-left ease .3s, padding-right ease .3s, color ease .7s;
}
```

<script src="https://kit.fontawesome.com/f3ae6d3fea.js" crossorigin="anonymous"></script>


## R Markdown

This is an <ins>R Markdown document</ins>. Markdown <ins>is</ins> a <del>simple</del> formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.`r trackchanger::comment("test")`

When you click the **Knit** <del>button</del> a document will be <del>generated</del> that includes both <del>content</del> as well as the output of any embedded R code chunks within the document. You can <del>embed</del> an R code chunk like this:

```{r cars}
summary(cars)
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
